---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# checkout

<!-- badges: start -->
[![R-CMD-check](https://github.com/maurolepore/checkout/workflows/R-CMD-check/badge.svg)](https://github.com/maurolepore/checkout/actions)
[![Codecov test coverage](https://codecov.io/gh/maurolepore/checkout/branch/main/graph/badge.svg)](https://codecov.io/gh/maurolepore/checkout?branch=main)
[![CRAN status](https://www.r-pkg.org/badges/version/checkout)](https://CRAN.R-project.org/package=checkout)
<!-- badges: end -->

The goal of this package is to checkout a set of git repositories in a way
similar to <https://github.com/actions/checkout>, to reproduce locally what you
may usually do in GitHub actions. It is most useful to test locally the latest
commit of the working directory in the context of the master branch of one or
multiple other repositories.

## Installation

You can install the development version of checkout from GitHub with:

``` r
# install.packages("devtools")
devtools::install_github("maurolepore/checkout")
```

## Example

```{r}
library(checkout)
library(magrittr)

# Helper
walk <- function(x, f, ...) {
  lapply(x, f, ...)
  invisible(x)
}
```

`git_walk()` and `git_map()` help you work with multiple Git repositories at
once. `git_walk()` is primarily called for its side effects; here we use it to
setup two minimal repositories.

```{r}
repos <- file.path(tempdir(), paste0("repo", 1:2))
repos %>% walk(dir.create)
repos %>% file.path("a-file.txt") %>% walk(file.create)
repos

repos %>%
  git_walk("init --initial-branch=main") %>%
  git_walk("config user.name Jerry") %>%
  git_walk("config user.email jerry@gmail.com") %>%
  git_walk("add .") %>%
  git_walk("commit -m 'Add a-file.txt'") %>%
  # Each repo now has a commit
  git_walk("log --oneline -n 1 --decorate", verbose = TRUE)
```

* `checkout()` is inspired by the `ref` argument of
<https://github.com/actions/checkout> and helps work locally in a way similar to
GitHub actions. If we set the directory at `repo1`, it stays at the branch `pr`,
whereas the `repo2` changes to the branch `master` (or `main`).

```{r}
oldwd <- getwd()
setwd(repos[[1]])

repos %>% git_walk("checkout -b pr")

# Compare before and after `checkout()`
repos %>% git_walk("branch", verbose = TRUE)
repos %>% checkout()
repos %>% git_walk("branch", verbose = TRUE)

# Cleanup
setwd(oldwd)
repos %>% walk(unlink, recursive = TRUE)
```
