---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# checkout

<!-- badges: start -->
<!-- badges: end -->

The goal of this package is to checkout a set of git repositories in a way
similar to <https://github.com/actions/checkout>, to reproduce locally what you
may usually do in GitHub actions. It is most useful to test locally the latest
commit of the working directory in the context of the master branch of one or
multiple other repositories.

## Installation

You can install the development version of checkout from GitHub with:

``` r
# install.packages("devtools")
devtools::install_github("maurolepore/checkout")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r}
library(checkout)
library(gert)
```

Setup two minimal repositories.

```{r}
repo_a <- file.path(tempdir(), "repo_a")
dir.create(repo_a)
file.create(file.path(repo_a, "a-file.txt"))
git_init(repo_a)
git_add(".", repo = repo_a)
git_commit_all("New file", repo = repo_a)

repo_b <- file.path(tempdir(), "repo_b")
dir.create(repo_b)
file.create(file.path(repo_b, "a-file.txt"))
git_init(repo_b)
git_add(".", repo = repo_b)
git_commit_all("New file", repo = repo_b)
```

If we set the directory at `repo_a`, it stays at the branch `pr`, whereas the `repo_b` changes to the branch `master` (or `main`).

```{r}
setwd(repo_a)

gert::git_branch_create("pr", checkout = TRUE, repo = repo_a)
gert::git_branch_create("pr", checkout = TRUE, repo = repo_b)

# Before
gert::git_branch(repo_a)
gert::git_branch(repo_b)

checkout(c(repo_a, repo_b))

# After
gert::git_branch(repo_a)
gert::git_branch(repo_b)
```

This behaviour is inspired by the `ref` argument of <https://github.com/actions/checkout> and helps work locally in a way similar to GitHub actions.
